%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%% CV Jakša Tomović 06/2019 %%%%%%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\PassOptionsToPackage{dvipsnames}{xcolor}
\documentclass[10pt,a4paper]{../altacv}

\usepackage[utf8]{inputenc} % Required for inputting international characters
\usepackage[T1]{fontenc} % Output font encoding for international characters

%Layout
\geometry{left=1cm,right=9cm,marginparwidth=6.8cm,marginparsep=1.2cm,top=1.25cm,bottom=1.25cm,footskip=2\baselineskip}

%Packages
\usepackage[utf8]{inputenc}
\usepackage[T1]{fontenc}
\usepackage[default]{lato}
\usepackage{hyperref}

%Colors

% old
%\definecolor{accent}{HTML}{000e17}
%\definecolor{heading}{HTML}{000e17}
%\definecolor{emphasis}{HTML}{696969}
%\definecolor{body}{HTML}{01415f}

\definecolor{accent}{HTML}{000e17}
\definecolor{heading}{HTML}{0077b5}
\definecolor{emphasis}{HTML}{696969}
\definecolor{body}{HTML}{000e17}

\colorlet{heading}{heading}
\colorlet{accent}{accent}
\colorlet{emphasis}{emphasis}
\colorlet{body}{body}

\hypersetup{%
	colorlinks=false,
	urlbordercolor=white
}

\renewcommand{\itemmarker}{{\small\textbullet}}
\renewcommand{\ratingmarker}{\faCircle}

\begin{document}
\name{Niels Reijers}
\tagline{Staff / Lead Software Engineer}
%\photo{2.5cm}{BrunoAlves}
\personalinfo{
	\begin{tabularx}{\linewidth}{@{} l X r @{}}
		\email{nielsreijers@gmail.com} &
		\github{\href{https://www.github.com/nielsreijers}{github.com/nielsreijers}} &
		\homepageright{\color{heading}\href{https://www.nielsreijers.com/cv/NielsReijers-full-version.pdf}{www.nielsreijers.com/cv-full-version.pdf}} \\
		\phone{+886 975 140 428} &
		\linkedin{\href{https://www.linkedin.com/in/niels-reijers-4609602}{linkedin.com/in/niels-reijers-4609602}} &
	\end{tabularx}
}

\begin{fullwidth}
\makecvheader

\begin{itemize}
\item Lead developer with 25+ years of experience evolving legacy systems and architecting large-scale solutions from initial design through full implementation.
\item PhD in computer science from National Taiwan University. Published in the field’s top conference. 
\end{itemize}

\end{fullwidth}

\small

\cvsection[page1sidebar]{Experience}

\medskip

\cvexperience{Senior Software Engineer}{Proton Mail}{Aug 2024 -- Ongoing}{Taipei, Taiwan / Rotterdam, The Netherlands}

\begin{itemize}
 	\item Building Rust backend services for Proton’s Lumo platform, covering LLM interfaces, tool integration, and prompt optimization, with a focus on reliability and system robustness.
	\item Shaped architecture and prompt design for an AutoGen-based framework enabling LLM-driven agentic task automation.
\end{itemize}

Traffic Analysis \& DDoS Protection:
\begin{itemize}
	\item Scaled ClickHouse-based traffic analysis pipelines, increasing DDoS protection capacity 5× by isolating it from heavy analytics queries.
	\item Improved root-cause analysis for traffic anomalies, reducing time to diagnosis.
\end{itemize}

\medskip

\cvtag{Rust}
\cvtag{vLLM}
\cvtag{ClickHouse}
\cvtag{Datadog Vector}
\cvtag{Python}

\medskip\cvexperience{Staff Software Engineer}{DSW Health Insurance (contract)}{Jun 2011 -- Apr 2025}{Schiedam, The Netherlands}

After leaving DSW to study Chinese and pursue a PhD, I was given the opportunity to combine this with contract work, from 2016 as Staff Software Engineer. This privilege was not typically offered to other employees.

\medskip

\begin{itemize}
	\item Designed and implemented multiple production systems; acted as a go-to troubleshooter across teams.
	\item Focused on automation, observability, and performance optimization.
	\item Initiated high-impact projects, including:
	\begin{itemize}
		\item[-] Company-wide service observability, enabling real-time system insight.
		\item[-] Migration from script-based deployments to a convention-over-configuration system, improving reliability and developer efficiency.
	\end{itemize}
\end{itemize}

\medskip

\cvtag{C\#}
\cvtag{MS SQL Server}
\cvtag{PowerShell}
\cvtag{Python}
\cvtag{Jupyter}

\medskip\medskip\cvexperience{Postdoctoral Researcher}{National Taiwan University / Academica Sinica}{Feb 2019 -- May 2021}{Taipei, Taiwan}
%Collaborated with professor Chih-Wen Hsueh at NTU on a novel block chain, and professor Yuh-Jye Lee at Sinica on a project to correct online disinformation.

\medskip\medskip\cvexperience{Doctoral Candidate}{Intel-NTU Connected Context Computing Center}{Sep 2011 -- Apr 2018}{Taipei, Taiwan}

Improved the state of the art for Java VMs for resource-constrained IoT devices:

\medskip

\begin{itemize}
	\item Improved performance to close to optimized C, thus reducing energy consumption, through on-device ahead-of-time compilation to native code.
	\item Provided a platform independent and sandboxed environment to protect devices from malicious code.
\end{itemize}

\medskip

Published the results in the field's top conference, SenSys 2018.

\medskip

\cvtag{C}
\cvtag{Embedded systems}
\cvtag{AVR assembly}
\cvtag{Java}
\cvtag{JVM bytecode}

\medskip\medskip\cvexperience{Lead Developer}{DSW Health Insurance}{Apr 2005 -- Nov 2009}{Schiedam, The Netherlands}

Lead the development of the new claims processing system as lead developer.

\medskip

\begin{itemize}
	\item Delivered on time, running reliably since 2009 and proven to be very maintainable, despite being the company's most complex system.
	\item Produced several spin-off products that became a company-wide standard for other teams, leading to improved efficiency and standardization.
\end{itemize}

\medskip

%\cvtag{C\#}
%\cvtag{MS SQL Server}

\end{document}
